Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-13 paper/section_3_model.tex
Rearrange figures
Cite pointer-generator paper
Rename copying mechanism

For the image, we feed it through a pretrained ResNet-152 model
\cite{He2016ResNet} and use the output of the final block, just before the
pooling layer, as the image embedding $\bx_I \in \mathbb{R}^{2048 \times 7
\times 7}$. The embedding forms a 7 by 7 block, allowing the transformer to
attend to 49 different patches in the image.

@@

Let $\bh_t$ be the current hidden state. We first do a linear projection of
$\bh_t$ and the image embedding $\bx_I$ into a query, key, and value, so that
all three have the same dimension:
\begin{IEEEeqnarray*}{lCl}
   \bq_T &=& W_{Iq} \, \bh_t \\
   \bk_T &=& W_{Ik} \, \bx_I \\
   \bv_T &=& W_{Iv} \, \bx_I
\end{IEEEeqnarray*}
Then the attended image $\bx_I'$ is the weighted sum of the values, where the weights are
obtained from the dot product between the key and value:
\begin{IEEEeqnarray*}{lCl}
   \bx_I' &=& \text{softmax}\left( \bq \bk^T \right) \bv
\end{IEEEeqnarray*}
We use the same attention mechanism to obtain the attended article $\bx_T'$
and the attended face $\bx_F'$. These three are then concatenated and fed
through a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \bx_C' &=& [\bx_I', \bx_T', \bx_F'] \\
   \bx_O &=& \text{LayerNorm}(X_C + W_O \, \text{ReLU}(W_C \, \bx_C' + \bb_C) + \bb_O)
\end{IEEEeqnarray*}

@@

>>>>

For the image, we feed it through a pretrained ResNet-152 model
\cite{He2016ResNet} and use the output of the final block, just before the
pooling layer, as the image embedding $\bx_I \in \mathbb{R}^{2048 \times 49}$.
The embedding forms a 7 by 7 block, allowing the transformer to attend to 49
different patches in the image.

@@

Let $\bh_t$ be the current hidden state. We first do a linear projection of
$\bh_t$ and the image embedding $\bx_I$ into a query, key, and value, so that
all three have the same dimension:
\begin{IEEEeqnarray*}{lCl}
   \bq_T &=& \bW_{Iq} \, \bh_t \\
   \bk_T &=& \bW_{Ik} \, \bx_I \\
   \bv_T &=& \bW_{Iv} \, \bx_I
\end{IEEEeqnarray*}
Then the attended image $\bx_I'$ is the weighted sum of the values, where the weights are
obtained from the dot product between the key and value:
\begin{IEEEeqnarray*}{lCl}
   \bx_I' &=& \text{softmax}\left( \bq \bk^T \right) \bv
\end{IEEEeqnarray*}
We use the same attention mechanism to obtain the attended article $\bx_T'$
and the attended face $\bx_F'$. These three are then concatenated and fed
through a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \bx_C' &=& [\bx_I', \bx_T', \bx_F'] \\
   \bx_O &=& \text{LayerNorm}(X_C + \bW_O \, \text{ReLU}(\bW_C \, \bx_C' + \bb_C) + \bb_O)
\end{IEEEeqnarray*}

@@

\subsubsection{Copying with Multi-headed Attention}

Inspired by pointer-generator networks \cite{See2017GetTT}, we introduce
a copying mechanism using multi-headed attention.

### 2019-11-13 paper/section_5_experiments.tex
Rename copying mechanism

In all experiments, we use Adam \cite{Kingma2015Adam} with the weight decay fix
\cite{Loshchilov2018DecoupledWD} to optimize the models. We use the following
parameters: $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$, and a weight
decay of $10^{-5}$. We clip the gradient norm at 0.1. All models see the same
number of training examples, which is 6.6 million. This is equivalent to 16
epochs through GoodNews and 9 epochs through NYTimes800k. We warm up the
learning rate in the first 5\% of the training steps to $10^{-4}$, and
afterward decays it linearly. Training the full model takes 5 days on one Titan
V GPU.

@@

\begin{table}[t]
	\caption {Model complexity}
	\label{tab:models}
	\centering
	\begin{tabularx}{\linewidth}{Xc}
		\toprule
        & No. of Parameters \\
      \midrule
      LSTM + GloVe & 157M \\
      Transformer + GloVe & 148M \\
      LSTM + weighted RoBERTa & 159M \\
      \midrule
      Transformer + RoBERTa & 154M \\
      \quad + weighted RoBERTa & 154M \\
      \quad\quad + face attention & 171M \\
      \quad\quad\quad + copy mechanism & 207M \\
		\bottomrule
	\end{tabularx}
\end{table}

>>>>

In all experiments, we use Adam \cite{Kingma2015Adam} with the weight decay fix
\cite{Loshchilov2018DecoupledWD} to optimize the models. We use the following
parameters: $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$, and a weight
decay of $10^{-5}$. We clip the gradient norm at 0.1. All models see the same
number of training examples, which is 6.6 million. This is equivalent to 16
epochs through GoodNews and 9 epochs through NYTimes800k. We warm up the
learning rate in the first 5\% of the training steps to $10^{-4}$, and decays
it linearly afterwards. Training is done with mixed precision to reduce the
memory footprint. The full model takes 5 days to train on one Titan V GPU.

@@

\begin{table}[t]
	\caption {Model complexity}
	\label{tab:models}
	\centering
	\begin{tabularx}{\linewidth}{Xc}
		\toprule
        & No. of Parameters \\
      \midrule
      LSTM + GloVe & 157M \\
      Transformer + GloVe & 148M \\
      LSTM + weighted RoBERTa & 159M \\
      \midrule
      Transformer + RoBERTa & 154M \\
      \quad + weighted RoBERTa & 154M \\
      \quad\quad + face attention & 171M \\
      \quad\quad\quad + copying & 207M \\
		\bottomrule
	\end{tabularx}
\end{table}
